Using reference models in feature selection \vspace{.1in}

### 2019-12-04 paper/ref_approach.tex
clean up Appendix A

As an another example, let us consider a candidate submodel in a
feature selection process and let us refer to the parameter
distribution of the submodel by $\pi$ and to the induced predictive
distribution by $q_{\pi}(\tilde{y})$. We would like to choose $\pi$ so
that $q_{\pi}(\tilde{y})$ maximises some predictive performance
utility, for example, the expected log-predictive density (elpd)
defined as: \
\begin{equation}\label{eq:elpd}
\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y},
\end{equation}
where $p_{t}(\tilde{y})$ denotes the (usually unknown) true generating
mechanism of future data $\tilde{y}$. If we refer to the posterior
predictive distribution of a reference model with $p(\tilde{y}|D)$,
where $D$ stands for the data on which we conditioned on, we can
approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true
data generation mechanism $p_{t}(\tilde{y})$. The maximisation of the
elpd using the reference model predictive distribution is equivalent
to the minimisation of the Kullback-Leibler (KL) divergence from the
reference model's predictive distribution to the submodel's predictive
distribution: \
\begin{equation} \label{proj_as_filter}
\underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p(\tilde{y}|D)d\tilde{y} \leftrightarrow \underset{\pi}{\text{min}} \; \text{KL}[p(\tilde{y}|D)||q_{\pi}(\tilde{y})] 
\end{equation}
The term on the right-hand side of Equation \eqref{proj_as_filter}
describes what is referred to as the projection of the predictive
distribution, which is the general idea behind the projection
predictive approach \cite[see][]{paper:projpred}. Again the reference
model is acting as a filter, or substitute, on data.

Relying on the idea of the reference model as a noise-filter, a
generic reference model approach, which can be used on top of any
feature selection procedure, consists of simply substituting the
target observations with corresponding point predictions of the
reference model, for instance, the posterior predictive
means. Afterwards, any method for feature selection can be used. We do
not argue that such a reference model approach should necessarily be
used as is for feature selection in real applications. There are
several more sophisticated reference model approaches available in the
literature \cite[see,
e.g.][]{paper:projpred,paananen2017variable,paul2008preconditioning},
which are likely to yield even better results. Rather, the reason for
focusing on this simple version is to enable a fair comparison between
a reference model and a purely data based approach when otherwise
using the same selection procedures. Other kinds of comparisons, as
the one presented in Section \ref{intro-example}, work well as
motivational examples but lack in terms of generality since the
presence or absence of a reference model is not the only aspect
differentiating the two procedures.
% We will come back to the more
% general comparison in Section \ref{comparison}.

As a motivational example to the implications of using a reference
model in feature selection problems, we show its application in the
form of the projection predictive approach, which uses the reference
model to project the posterior draws to the submodels
\citep{paper:original_proj}. The \texttt{R}-package \texttt{projpred}
(available at \url{https://CRAN.R-project.org/package=projpred})
implements the projection in case of submodels in the family of the
generalised linear models and, additionally, it provides a framework
to choose the optimal submodel size through a predictive utility
comparison between the submodels and the reference model.

We now summarise the workflow of the projection predictive approach in
the particular case of the draw-by-draw projection \cite[original
formulation by][]{paper:original_proj}, following
\cite{paper:projpred}. Suppose we have observed $n$ statistical units
with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed
covariates for which we want to obtain a minimally relevant
subset. Than, the main steps are the following:
\begin{enumerate}
\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ draws from the reference model posterior.
\item Rank the covariates according to their relevance using some
  heuristics and consider as candidate submodels only those which
  preserve this order, starting from including only the highest ranked
  covariate (the submodels are then naturally identified by their
  model size). This is not strictly necessary but reduces the number
  of submodels to consider in the following steps.
\item For each submodel, project the reference model posterior draws as follows:
\begin{equation}\label{eq:draw_by_draw}
\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left( p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right), \quad s=1,\ldots,S \,,
\end{equation}
where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the
predictive distribution of the reference model with parameters fixed
at $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariate
values related to the statistical unit (identified by the subscript
$i$), whereas $q(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the
predictive distribution of the submodel. The projected draws
$\boldsymbol{\theta}_{\perp}^{s}$ then present the projected posterior
for the submodel.
\item For each submodel (size), test the predictive performance, for example, via cross-validation.
\item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.
\end{enumerate}

Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem
in general, but in the special case of submodels for the family of
generalised linear models, \eqref{eq:draw_by_draw} reduces to a
maximum likelihood estimation problem, which can be easily optimised
\citep{paper:original_proj}. For further details on the projective
prediction workflow and implementation see \cite{paper:projpred}.

>>>>

\subsection*{Appendix A: Projective Predictions}

The projective prediction (projpred) approach was developed and is thoroughly
 described in \cite{paper:projpred}. In this appendix, we provide a high level
  description of the method so that readers do not need to study \cite{paper:projpred} in detail
in order to understand the main ideas behind projpred.

 Let us refer to the parameter
distribution of a given candidate submodel by $\pi$ and to the induced predictive
distribution by $q_{\pi}(\tilde{y})$. We would like to choose $\pi$ so
that $q_{\pi}(\tilde{y})$ maximises some predictive performance
utility, for example, the expected log-predictive density (elpd)
defined as: \
\begin{equation}\label{eq:elpd}
\text{elpd}[q_{\pi}]=\int \text{log}\,q_{\pi}(\tilde{y})p_{t}(\tilde{y})d\tilde{y},
\end{equation}
where $p_{t}(\tilde{y})$ denotes the (usually unknown) true generating
mechanism of future data $\tilde{y}$. If we refer to the posterior
predictive distribution of a reference model with $p(\tilde{y}|D)$,
where $D$ stands for the data on which we conditioned on, we can
approximate \eqref{eq:elpd} using $p(\tilde{y}|D)$ instead of the true
data generation mechanism $p_{t}(\tilde{y})$. The maximisation of the
elpd using the reference model's predictive distribution is equivalent
to the minimisation of the Kullback-Leibler (KL) divergence from the
reference model's predictive distribution to the submodel's predictive
distribution: \
\begin{equation} \label{proj_as_filter}
\underset{\pi}{\text{max}} \; \int \text{log}\,q_{\pi}(\tilde{y})p(\tilde{y}|D)
\, \text{d} \tilde{y} 
\quad \Leftrightarrow \quad 
\underset{\pi}{\text{min}} \; \text{KL}[p(\tilde{y}|D) \; || \; q_{\pi}(\tilde{y})] 
\end{equation}
The term on the right-hand side of Equation \eqref{proj_as_filter}
describes what is referred to as the projection of the predictive
distribution, which is the general idea behind the projection
predictive approach \cite[see][]{paper:projpred}. 
We now summarise the workflow of the projection predictive approach in
the particular case of the draw-by-draw projection \cite[original
formulation by][]{paper:original_proj}, following
\cite{paper:projpred}. Suppose we have observed $n$ statistical units
with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed
covariates for which we want to obtain a minimally relevant
subset. Than, the main steps are the following:
\begin{enumerate}
\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of $S$ draws from the reference model's posterior.
\item Rank the covariates according to their relevance using some
  heuristics and consider as candidate submodels only those which
  preserve this order, starting from including only the highest ranked
  covariate. The submodels are then naturally identified by their
  model size. This step is not strictly necessary but reduces the number
  of submodels to considered in the following steps and thus reduces computation time.
\item For each submodel $\pi$ selected in Step 2, project each of the reference model's posterior draws $\boldsymbol{\theta}_{*}^{s}$ as follows:
\begin{equation}\label{eq:draw_by_draw}
\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta^{s}}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL} \left[ p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\;||\;q_\pi(\tilde{y}_{i}|\boldsymbol{\theta}^{s}) \right],
\end{equation}
where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the
predictive distribution of the reference model with parameters fixed
at $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariate
values related to the statistical unit (identified by the subscript
$i$), whereas $q_\pi(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ is the
predictive distribution of the submodel. The projected draws
$\boldsymbol{\theta}_{\perp}^{s}$ then present the projected posterior
for the submodel.
\item For each submodel (size), test the predictive performance for a chosen predictive utility score, for example, via cross-validation.
\item Choose the smallest submodel (size) that is sufficiently close to the reference model's predictive utility score.
\end{enumerate}

In general, Expression \eqref{eq:draw_by_draw} is not an easy optimisation problem
However, in the special case of the submodels being
generalised linear models with a likelihood coming from the exponential family, \eqref{eq:draw_by_draw} reduces to a
maximum likelihood estimation problem, which can be easily solved
\citep{paper:original_proj}. For further details on the projective
prediction workflow and implementation see \cite{paper:projpred}.
